Global phase diagram and possible quantum spin liquid in the extended triangular lattice model

### 2019-12-04 paper/paper.tex
20191204 22:06

\section{Introduction}
Geometrical frustration, which arises when the lattice geometry gives rise to constraints on the system Hamiltonian that cannot be simultaneously satisfied, plays an important role in various kinds of magnetic systems. In particular, antiferromagnets on the triangular lattice is a typcial example of such geomtrical frustrated spin systems. Anderson proposed that a fully disordered resonating-valence-bond (RVB) state may be the ground state of the antiferromagnetic Heisenberg model on triangular lattice. However, exchange frustation in systems with strongly anisotropic magnetic exchange has been shown  tobe another avenue to explore the QSL state.

>>>>

\section{Introduction}
Geometric frustration, which arises when the lattice geometry gives rise to constraints on the system Hamiltonian that cannot be simultaneously satisfied, plays an important role in various kinds of magnetic systems. In particluar, antiferromagnets on the triangular lattice are typical examples of such geometric frustated spin systems and have attracted numerous interest in condensed matter physics. For nearest-neighbor antiferromagetic Heisenberg model on triangular lattice, Anderson proposed that a fully disordered resonating-valence-bond (RVB) state may be the ground state. However, lots of studies point to a 120$^\circ$ N\'{e}el-ordered ground state. It is thus desirable to include next-nearest-neighbor interactions to introduce further frustration. After considering the next-nearest-neighbor interactions, the system has a much richer phase diagram incluing a N\'{e}el phase, a phase with spin-wave selection of nontrivial ground states and a phase with incommensurate long-range order. All these studies have revealed that geometric frustated systems show quite different behavior from that of the non-frustated system. \textcolor{red}{$\cdots\cdots$}

Recently however, exchange frustation in systems with strongly anisotropic magnetic exchange has been shown to be another promising approach to explore exotic quantum spin states. Like Geometrical frustation, the effect of exchange frustration is to prevent the formation of long range magnetic order and given raise to a residual ground-state entropy. \textcolor{red}{$\cdots\cdots$}

On the experimental side, a variety of triangular magnets such YbMgGaO$_2$, \emph{AReCh}$_2$ (A=alkali or monovalent ions, Re=rare-earth, Ch=O, S,Se) have been synthesized and explored by magnetic susceptibility and heat capacity measurements. The lack of signature for long-range magnetic order and spin freezing down to very low temperature implies their candidacy for quantum spin liquid state. \textcolor{red}{$\cdots\cdots$}

Inspired by previous theoretical and experimental works, we study the J-K-$\Gamma$ model Hamiltonian on the triangular lattice. To the best of our knowledge, no exact solution of the spin-$1/2$ Kitaev or $\Gamma$ model on the triangular lattice has been obtained so far. Therefore, it remains conceptually interesting to investigate whether the QSL could exist as a possible ground state of the triangular J-K-$\Gamma$ model. \textcolor{red}{$\cdots\cdots$}

In this paper, be combining the classical Monte Carlo simulation and exact diagonalization (ED) calculation, we map out the global phase diagram of the J-K-$\Gamma$ model. \textcolor{red}{$\cdots\cdots$}

The rest of the paper is organized as follows: \textcolor{red}{$\cdots\cdots$}
